Engineering momentum profiles of cold-atom beams

### 2019-07-11 Paper/pra_resub/paper.tex
added in artems change to new intro paragraph

Other studies related to the engineering of atomic beams have focused on the  outcoupling of atoms in an atomic wave guide to a Bose-Einstein condensate using rf fields \cite{PhysRevLett.97.200402, PhysRevA.80.041605, buning2010slow} or on controlling the transmission of atoms with careful manipulation of an optical lattice \cite{PhysRevLett.84.399, PhysRevLett.107.230401, PhysRevA.92.033614}. In contrast, the current article proposes a method for engineering atomic beams by coupling a trapped gas of atoms to a combination of individually tuned lasers. Moreover, the proposed scheme is generic in the sense that one can approximately produce arbitrary desired momentum profiles of the transmitted atom beam.

>>>>

Other studies related to the engineering of atomic beams have focused on  the  outcoupling  of  atoms  from a Bose-Einstein condensate \cite{PhysRevLett.97.200402, PhysRevA.80.041605, buning2010slow} or on controlling the transmission of atoms with careful manipulation of an optical lattice \cite{PhysRevLett.84.399, PhysRevLett.107.230401, PhysRevA.92.033614}. In contrast, the current article proposes a method for engineering atomic beams by coupling a trapped gas of atoms to a combination of individually tuned lasers. Moreover, the proposed scheme is generic in the sense that one can approximately produce arbitrary desired momentum profiles of the transmitted atom beam.
